Online reprocessing simulation for thorium-fueled molten salt breeder reactor

### 2017-07-25 discussion.tex
ANS revisions

\section{Discussion}
This work demonstrated that, given infinite
reprocessing and \gls{MOX} fabrication capacities,
France can transition into a fully \gls{SFR} fleet
with installed capacity of 60,000 MWe by 2076.
The initial fuel demand is filled by \gls{MOX} from
reprocessed \gls{SNF}, which later on
is met by \gls{MOX} created from recycled \gls{MOX}.

Since most \gls{EU} nations do not have an operating \gls{SNF}
repository or a management plan, they have a strong incentive
to send all their \gls{SNF} to France. France has a financial
incentive (compensation from other nations) to take this fuel,
and since reuse of spent fuel from
other nations will allow France to meet their MOX demand
without new construction of \glspl{LWR}.

>>>>

\section{Discussion}
This work demonstrated that, given infinite
reprocessing and \gls{MOX} fabrication capacities,
France, by receiving \gls{UNF} from other \gls{EU} nations,
can transition into a full \gls{SFR} fleet
with installed capacity of 60,000 MWe by 2076.
The initial fuel demand is filled by \gls{MOX} from
reprocessed \gls{UNF}, which later on
will be met by \gls{MOX} created from recycled \gls{MOX}.

Since most \gls{EU} nations do not have an operating \gls{UNF}
repository or a management plan, they have a strong incentive
to send all their \gls{UNF} to France. Especially, the nations
with aggressive nuclear reduction can phase out nuclear
without constructing a High Level Waste repository. France has a financial
incentive to take this fuel, since reuse of used fuel from
other nations will allow France to meet their MOX demand
without new construction of \glspl{LWR}.

### 2017-07-25 introduction.tex
ANS revisions

\section{Abstract}
The French strategy recommended by 2012-2015 Commission Nationale d'Evaluation reports
\cite{cne2_noauthor_2015} emphasizes preparation for a transition from \glspl{LWR} to \glspl{SFR}.
This paper uses \Cyclus to explore the feasibility of using \gls{SNF}from other EU nations
for French transition into a \gls{SFR} fleet without additional construction of \glspl{LWR}.
A \Cyclus simulation is run from 1950 to 2160 for EU to track the \gls{SNF} mass
and to determine the necessary reprocessing and \gls{MOX} fabrication capacity to support
the transition into \glspl{SFR}. The study concludes that France can avoid deployment
of additional \glspl{LWR} by accepting \gls{SNF} from other EU nations.

\section{Introduction}
This paper uses \Cyclus, the agent-based simulator \cite{huff_fundamental_2016} to analyze
the future nuclear inventory in the European Union. This paper focuses on the spent fuel
inventory in \gls{EU} member states in 2050, and analyzes various potential strategies of spent fuel
management.
A major focus of this paper is to determine the extent to which France has an incentive
to receive all the \gls{SNF} from \gls{EU} nations to create \gls{MOX}.
The \gls{MOX} created will fuel French transition to a \gls{SFR} fleet
and may allow France to avoid building additional \glspl{LWR}.

Past research, which focuses mostly on France, has made the assumptions that additional \glspl{LWR},
namely \glspl{EPR} are constructed in order to supply \gls{SNF} required
for \gls{MOX} production \cite{carre_overview_2009, martin_symbiotic_2007, freynet_multiobjective_2016}.
There has been little attention in reprocessing legacy \gls{SNF} from other
EU nations to produce \gls{MOX} for the newly deployed \glspl{SFR}.
The present work finds that this collaborative strategy can reduce the
need to construct additional \glspl{LWR} in France.

A \Cyclus simulation is run to calculate
how much spent fuel is created from \gls{EU} nations from 1970 to 2050, as well as the amount
of \gls{MOX} that can be created with the \gls{SNF} inventory.
The paper assumes a once-through cycle for all 
\gls{EU} nations with the exception of France. France can reprocess spent \gls{UOX} and \gls{MOX} to
produce \gls{MOX} from reprocessed plutonium and depleted uranium (tails).
The simulation assumes \gls{MOX} is reprocessed infinitely. 
After obtaining the \gls{SNF} inventory of all \gls{EU} in 2050, a separate
simulation is run where the \gls{SNF} inventory is reprocessed and
used as fuel for the newly deployed \gls{SFR} reactors.
\gls{SFR} reactors in this paper models after the ASTRID reactor,
and use \gls{MOX} fuel created from 9\% reprocessed plutonium
and 91\% tailings to a burnup
of approximately 100 GWdth/t. The high burnup allows enough production of plutonium
for an equivalent mass of \gls{MOX}, if mixed with tailings.  Eventually,
the used \gls{UOX} inventory will be exhausted, and the \glspl{SFR} must be
fueled by \gls{MOX} created from recycled \gls{MOX}.
It is assumed that \glspl{SFR} are available for deployment
from 2040.

\section{Methodology}
The work relies on \Cyclus, an agent-based simulator, to simulate the nuclear fuel cycle
and track material flows in \gls{EU} nations. The \gls{PRIS} open-source 
database from \gls{IAEA} was used to populate the simulation with deployment 
information. That database is imported as a csv file, listing the country, reactor unit, type, net capacity (MWe), status,
operator, construction date, first criticality date, first grid date, commercial date, shutdown
date (if applicable), and unit capacity factor for 2013. Then only the \gls{EU} countries are extracted
from the csv file. A python script is written up to generate a \Cyclus input file from the csv file,
which lists the individual reactor units as agents. After running the \Cyclus input file,
the output file is analyzed by another python script.

First, a simulation is run from 1970 to 2050 to calculate the mass of 
\gls{SNF} and depleted uranium (tails) \gls{EU} accumulates before 2050. 
The second simulation only looks at France, where France
uses the entire \gls{SNF} inventory from the previous
simulation to fuel
the newly deployed \glspl{SFR}. French \gls{SFR}s are deployed
to make up for the decommissioned capacity of \gls{LWR}s, to
remain a constant installed capacity of 60,000 MWe.

\subsection{Assumptions}
This paper makes the following assumptions:
\begin{itemize}
        \item \gls{SFR} technology available in 2040
        \item Decay has no effect on reprocessing viability
        \item Reactor construction is always completed on time 
        \item Unused separated uranium is stockpiled
        \item Nuclear power plants have a lifetime of 60 years, unless stated otherwise (early shutdown)
        \item (Only for SFR Case) French nuclear capacity remains constant at 60,000 MWe
        \item (Only for SFR Case) Infinite reprocessing and fabrication capacity
\end{itemize}

\subsection{Deployment Timeline}
Projections of future reactor deployment in this simulation were
assessed based on analysis from references such as \gls{PRIS} for reactors planned for construction \cite{iaea_pris_nodate},
and the World Nuclear Association and two other papers for future plans in EU nations
\cite{world_nuclear_association_nuclear_2017, joskow_future_2012, hatch_politics_2015}.
The projections extend to 2050 at the latest. This allows the simulation to take place from
1970 to 2050, the latest foreseeable future. The specific plans for each \gls{EU} nation are explained
in detail in later sections.

It is also assumed that all reactors that are 
currently operating have a lifetime of 60 years, unless their government plans
early shutdown. This will approximate when and how much \glspl{SFR} need to be built
to make up for the shutdown of \glspl{LWR}.

@@

From 2040, when \gls{SFR}s become available,
600-MWe \gls{SFR}s are deployed to make up for the 
decommissioned \gls{LWR} capacities.

@@

\begin{figure}[htbp!]
        \begin{center}
                \includegraphics[width=\columnwidth]{./images/french-transition/power_plot.png}
        \end{center}
        \caption{Timeseries of installed capacity of \gls{SFR}s}
        \label{fig:sfr_cap}
\end{figure}
\FloatBarrier

\begin{figure}[htbp!]
        \begin{center}
                \includegraphics[width=\columnwidth]{./images/french-transition/number_plot.png}
        \end{center}
        \caption{Timeseries of number of \gls{SFR}s}
        \label{fig:sfr_num}
\end{figure}
\FloatBarrier

\Cref{fig:sfr_cap} and \cref{fig:sfr_num} display
the \gls{SFR} number and capacity over time.
The sharp increase from 2035 to 2060 is due mainly to
French aggressive growth from 1975 to 2000.

\subsection{Depletion Calculations}
Depletion calculations of the nuclear fuel are recipe-based, such that a fresh 
and spent fuel recipe is used for each reactor type. To capture varying reactor 
capacity, a linear burnup model was assumed and extrapolated from the 
appropriate recipe. For example, a PWR of
1,000 MWe capacity has 193 assemblies of 3.2\% enriched
uranium fuel, with each assembly with a mass of 523.4 kg.
The core has a 18 month cycle, where one-third of the 
core (64 assemblies) are discharged per refueling. The refueling
is assumed to take 2 months to complete, during which the reactor
is shut down. For the \gls{SFR}, a model design is adopted from
Marsault–Marie-Sophie et al. \cite{marsaultmarie-sophie_pre-conceptual_2012}.

For the compositions of the fuel, a reference depletion calculation
from ORIGEN is used (see appendix). The recipe has also been used for
\cite{wilson_adoption_2009}.

\subsection{Scenario Descriptions}
The simulation follows the model fuel cycle, where a `source'
provides natural uranium, which is enriched by an 'enrichment'
facility to \gls{UOX}, while disposing enrichment waste (tailings)
to the 'sink' facility. The enriched \gls{UOX} is used
in the \gls{LWR}s and \gls{UOX} waste is produced. The spent fuel
is then reprocessed to separate plutonium and uranium.
The plutonium is mixed with depleted uranium (tails) to \gls{MOX}.
The reprocessed uranium is stockpiled. \gls{SNF} decay is assumed
to have no effect on reprocessing viability.

The second scenario estimates the \gls{SNF} inventory in \gls{EU} at 2050,
and reprocesses the \gls{SNF} to separate plutonium. The separated
plutonium is mixed with the depleted uranium inventory from 2050
to create \gls{MOX}, which is used in the \gls{SFR}s. The used
\gls{MOX} is also reprocessed to extract plutonium, which also
is mixed with depleted uranium to produce \gls{MOX}.

>>>>

\section{Abstract}
The French strategy recommended by 2012-2015 Commission Nationale d'Evaluation reports
\cite{noauthor_cne2_nodate} emphasizes preparation for a transition from \glspl{LWR} to \glspl{SFR}.
This paper uses \Cyclus to explore the feasibility of using \gls{UNF} from other EU nations
for French transition into a \gls{SFR} fleet without additional construction of \glspl{LWR}.
A \Cyclus simulation is run from 1950 to 2160 for EU to track the \gls{UNF} mass
and to determine the necessary reprocessing and \gls{MOX} fabrication capacity to support
the transition into \glspl{SFR}. The study concludes that France can avoid deployment
of additional \glspl{LWR} by accepting \gls{UNF} from other EU nations.

\section{Introduction}
This paper uses \Cyclus, the agent-based simulator \cite{huff_fundamental_2016} to analyze
the future nuclear inventory in the European Union. This paper focuses on the used fuel
inventory in \gls{EU} member states in 2050, and analyzes a potential strategy of used fuel
management.
A major focus of this paper is to determine the extent to which France has an incentive
to receive all the \gls{UNF} from \gls{EU} nations to create \gls{MOX}.
The \gls{MOX} created will fuel French transition to a \gls{SFR} fleet
and may allow France to avoid building additional \glspl{LWR}.

Past research, which focuses solely on France, has made the assumptions that additional \glspl{LWR},
namely \glspl{EPR} are constructed in order to supply \gls{UNF} required
for \gls{MOX} production \cite{carre_overview_2009, martin_symbiotic_2017, freynet_multiobjective_2016}.
There has been studies on implementation of partitioning and transmutation
in a regional (European) context, with \glspl{ADS} and Gen-IV reactors \cite{fazio_study_2013}.
There has been little attention in reprocessing legacy \gls{UNF} from other
EU nations to produce \gls{MOX} for the newly deployed \glspl{SFR}.
The present work finds that this collaborative strategy can reduce the
need to construct additional \glspl{LWR} in France.

\section{Methodology}
The work relies on \Cyclus, an agent-based simulator, to simulate the nuclear fuel cycle
and track material flows in \gls{EU} nations. The \gls{PRIS} open-source 
database from \gls{IAEA} was used to populate the simulation with deployment 
information. That database is imported as a csv file, listing the country, reactor unit, type, net capacity (MWe), status,
operator, construction date, first criticality date, first grid date, commercial date, shutdown
date (if applicable), and unit capacity factor for 2013. Then only the \gls{EU} countries are extracted
from the csv file. A python script is written up to generate a \Cyclus input file from the csv file,
which lists the individual reactor units as agents. After running the \Cyclus input file,
the output file is analyzed by another python script. All the scrips and data used
in this paper are available in \url{https://github.com/jbae11/transition-scenarios}.

Two \Cyclus simulations are run for this paper. 
The first simulation calculates
how much used fuel and tailings \gls{EU} nations accumulate from 1970 to 2050,
as well as the amount of \gls{MOX} that can be created with the \gls{UNF} inventory.
The paper models a once-through cycle for all 
\gls{EU} nations with the exception of France. France can reprocess used \gls{UOX} and \gls{MOX} to
produce \gls{MOX} from reprocessed plutonium and depleted uranium (tailings).
The simulation assumes \gls{MOX} is reprocessed infinitely.

After obtaining the \gls{UNF} inventory of all \gls{EU} in 2050, the second
simulation is run where the \gls{UNF} inventory is reprocessed and
used as fuel for the newly deployed \gls{SFR} reactors.
The \glspl{SFR} are deployed to make up for the decommissioned capacity
of \glspl{LWR} in France, to remain a constant installed capacity of $60,000$ MWe up to 2160.
\gls{SFR} reactors in this paper models after the ASTRID reactor,
and use \gls{MOX} fuel created from 11\% reprocessed plutonium
and 89\% tailings to a burnup
of approximately 100 GWdth/t. The high burnup allows breeding of plutonium.
Eventually, the entire fleet
of \glspl{SFR} are fueled by \gls{MOX} created from recycled \gls{MOX}.

\subsection{Assumptions}
This paper makes the following assumptions:
\begin{itemize}
	\item \gls{SFR} technology available for deployment in 2040
	\item Decay has no effect on reprocessing viability
	\item Reactor construction is always completed on time 
	\item Separated uranium is stockpiled
	\item \glspl{LWR} have a lifetime of 60 years, unless stated otherwise (early shutdown)
	\item Newly deployed \glspl{SFR} have a lifetime of 80 years.
	\item (Only for SFR Case) Reprocessing and \gls{MOX} fabrication begins in 2020.
	\item (Only for SFR Case) French nuclear capacity remains constant at 60,000 MWe
	\item (Only for SFR Case) Infinite reprocessing and fabrication capacity
\end{itemize}

\subsection{Deployment Timeline}
Projections of future reactor deployment in this simulation were
assessed based on analysis from references such as \gls{PRIS} for reactors planned for construction \cite{iaea_pris_nodate},
the World Nuclear Association and two other papers for future plans in EU nations
\cite{world_nuclear_association_nuclear_2017, joskow_future_2012, hatch_politics_2015}.
The projections extend to 2050 at the latest. This allows the simulation to take place from
1970 to 2050, the latest foreseeable future. The specific plans for each \gls{EU} nation are explained
in detail in later sections.

It is also assumed that all reactors that are 
currently operating have a lifetime of 60 years, unless their government plans
early shutdown. This will approximate when and how many \glspl{SFR} need to be built
to make up for the shutdown of \glspl{LWR}.

@@

From 2040, when \gls{SFR}s become available,
600-MWe \gls{SFR}s are deployed to make up for the 
decommissioned \gls{LWR} capacities. Note that a second
separate simulation is run to emphasize France apart from
all other EU nations.

@@

\begin{figure}[htbp!]
	\begin{center}
		\includegraphics[width=\columnwidth]{./images/french-transition/number_plot.png}
	\end{center}
	\caption{French Transition into an SFR Fleet}
	\label{fig:sfr_num}
\end{figure}
\FloatBarrier

\Cref{fig:sfr_num} displays
the French transition into \glspl{SFR} over time.
The steep transition from 2035 to 2060 is due mainly to
French aggressive growth from 1975 to 2000. Note the jump in
2040 is due to an attempt to make up for the gap between the
mass decommission of old \glspl{LWR} and the availability
of \glspl{SFR}.

\subsection{Depletion Calculations}
Depletion calculations of the nuclear fuel are recipe-based, such that a fresh 
and used fuel recipe is used for each reactor type.
For the compositions of the fuel, a reference depletion calculation
from ORIGEN is used (see \cref{tab:comp}). The recipe has also been used for
\cite{wilson_adoption_2009}.

\subsection{Scenario Descriptions}
The simulation follows the model fuel cycle, where a `source'
provides natural uranium, which is enriched by an 'enrichment'
facility to produce \gls{UOX}, while disposing enrichment waste (tailings)
to the 'sink' facility. The enriched \gls{UOX} is used
in the \gls{LWR}s and \gls{UOX} waste is produced. The used fuel
is then reprocessed to separate plutonium and uranium.
The plutonium is mixed with depleted uranium (tailings) to \gls{MOX}.
The reprocessed uranium is stockpiled. The cycle is illustrated in
\cref{diag:fc}.

The second scenario separates plutonium from the \gls{UNF}
inventory from the previous simulation. The separated
plutonium is mixed with the depleted uranium inventory from the previous simulation
to create \gls{MOX}, which is used in the \gls{SFR}s. The used
\gls{MOX} is also reprocessed to extract plutonium, which is also
mixed with depleted uranium to produce \gls{MOX}.

### 2017-07-25 results.tex
ANS revisions

\begin{table}[h]
	\centering
	\scalebox{0.86}{
		\begin{tabular}{|c|c|c|}
			\hline
			Category  & Value [t] & Specifics \\ \hline
			Total Natural U & 1,314,003 & \\ \hline
			Total UOX Usage  & 188,196  &  \\ \hline
			Total MOX Usage  & 118 & \\ \hline
			Total Spent UOX  & 183,992 & \\ \hline
			Total Spent MOX  & 0 & All is Reprocessed. \\ \hline
			Total Tailings  & 1,125,798 & \\ \hline
		\end{tabular}}
		\caption{Simulation Results}
		\label{tab:sim_result}
		\end {table}

@@

@@

\begin{figure}[htbp!]
	\begin{center}
		\includegraphics[width=\columnwidth]{./images/eu_future/power_plot.png}
	\end{center}
	\caption{Timeseries of installed nuclear capacity in \gls{EU}.}
	\label{fig:eu_pow}
\end{figure}

Figures \ref{fig:eu_num} and \ref{fig:eu_pow} display the
timeseries of number of reactors and installed capacity in \gls{EU}.

Figures \ref{fig:eu_tail} and \ref{fig:eu_snf} show the 
timeseries of mass of tailings and spent fuel accumulation in \gls{EU}.

\begin{figure}[htbp!]
	\begin{center}
		\includegraphics[width=\columnwidth]{./images/eu_future/tailings.png}
	\end{center}
	\caption{Timeseries of Tailings in the \gls{EU}.}
	\label{fig:eu_tail}
\end{figure}

\begin{figure}[htbp!]
	\begin{center}
			\includegraphics[width=\columnwidth]{./images/eu_future/snf.png}
	\end{center}
	\caption{Timeseries of Spent Nuclear Fuel in Sink.}
	\label{fig:eu_snf}
\end{figure}

\begin{table}[h]
	\centering
	\begin{tabular}{|c|c|c|}
		\hline
		Isotope & Mass Fraction in Spent Fuel [\%] & Quantity [t] \\ \hline
		Total & .9358 & 1,721.79 \\ \hline
		Pu238 & .0111 & 20.42 \\ \hline
		Pu239 & .518 & 953.07 \\ \hline
		Pu240 & .232 & 426.86 \\ \hline
		Pu241 & .126 & 231.82 \\ \hline
		Pu242 & .0487 & 89.6 \\ \hline
	\end{tabular}
	\caption{Plutonium From Spent Fuel}
	\label{tab:pu}
\end{table}

To create \gls{MOX}, ~9\% Pu and ~91\% depleted uranium is used.
Thus $1,721$ tons of plutonium yields $19,122$ tons of
\gls{MOX}. \Cref{tab:pu} lists the isotope, mass fraction,
and quantity of plutonium that can be obtained from the 2050 \gls{SNF} inventory.

@@

From Varaine et al., a French
ASTRID-type \gls{SFR} of capacity $600 MWe$ needs $1.225$ tons of
plutonium a year, with an initial plutonium loading of $4.9$ tons
\cite{marsaultmarie-sophie_pre-conceptual_2012}.
Thus, it can be assumed that the ASTRID reactor takes in $49$ tons of 
\gls{MOX}, and refuels a quarter of its fuel every year. Simply,
an ASTRID reactor needs $12.25$ tons of \gls{MOX} per year.

The number of SFR-years worth of fuel that can be created with
the \gls{SNF} from 2050 is $\frac{19,122t}{12.25} = 1,560 $,
assuming infinite reprocessing and \gls{MOX} fabrication capacity.

However, assuming that \gls{MOX} can be recycled indefinitely,
spent \gls{MOX} from an ASTRID reactor
contains enough plutonium to produce a \gls{MOX} fuel with
the same mass, if mixed with depleted uranium. 
Separating plutonium from spent \gls{MOX} from
an ASTRID reactor can create \gls{MOX} 
the mass of spent \gls{MOX}, given sufficient tailings supply.

The second scenario, with the tails and spent \gls{UOX}
inventory, evaluates if the French can transition into \gls{SFR}
without constructing additional \gls{LWR}s. This simulation
assumed infinite reprocessing and fabrication capacity.

\Cref{fig:fuel} shows the mass of \gls{MOX} used in the 
\gls{SFR}s separated by how they are made, over time.
Note that the mass of \gls{MOX} from the spent \gls{UOX}
stops increasing around 2050, which means that the spent
\gls{MOX} is enough to create the \gls{MOX} for the
\gls{SFR} fleet.

@@

\Cref{fig:pu_demand} shows the separated plutonium demand
for \gls{MOX} production to fuel the ASTRID reactors given the deployment schedule.

\begin{figure}[htbp!]
	\begin{center}
		\includegraphics[width=\columnwidth]{./images/french-transition/pu_total_demand.png}
	\end{center}
	\caption{Separated Plutonium demand for \gls{MOX} production}
	\label{fig:pu_demand}
\end{figure}

\begin{table}[h]
	\centering
	\scalebox{0.86}{
		\begin{tabular}{|c|c|c|}
			\hline
			Category [unit] & Value & Specifics \\ \hline
			Total MOX used [t] & 164,141 & \\ \hline
			Total MOX from UOX Waste [t] & 19,136.2  &   \\ \hline
			Total MOX from MOX Waste [t] & 145,004.8 & \\ \hline
			Total Tailings used [t] & 149,368.3 & \\ \hline
			Total legacy SNF reprocessed [t] & 183,992 & \\ \hline
		\end{tabular}}
		\caption {\gls{SFR} Simulation Results}
		\label{tab:sfr_sim_result}
\end {table}

>>>>

\begin{table}[h]
	\centering
	\scalebox{0.7}{
		\begin{tabular}{|c|c|c|c|}
			\hline
			Category & Unit & Value & Specifics\\ \hline
			Total UOX Usage & MTHM & 178,865 &  \\ \hline
			Total MOX Usage & MTHM & 8,909 & \\ \hline
			Total Used UOX Stored & MTHM & 157,472 & \gls{UNF} that are not reprocessed\\ \hline
			Total Used  MOX Stored & MTHM & 679 & \gls{UNF} that are not reprocessed \\ \hline
			Total Tailings & MTHM & 1,063,909 & \\ \hline
			Total Natural U Used & MTHM & 1,251,658 & \\ \hline
		\end{tabular}}
		\caption{Simulation Results for Historical Nuclear Operation of \gls{EU} Nations}
		\label{tab:sim_result}
		\end {table}

@@

		Figures \ref{fig:eu_num} and \ref{fig:eu_pow} display the
		timeseries of number of reactors and installed capacity in \gls{EU} nations.

@@

		\begin{figure}[htbp!]
			\begin{center}
				\includegraphics[width=\columnwidth]{./images/eu_future/power_plot.png}
			\end{center}
			\caption{Timeseries of installed nuclear capacity in \gls{EU}.}
			\label{fig:eu_pow}
		\end{figure}
		\FloatBarrier

		Figures \ref{fig:eu_tail} and \ref{fig:eu_snf} show the 
		timeseries of mass of tailings and used fuel accumulation in \gls{EU}.

		Figure \ref{fig:eu_fuel} shows the amount of fuel used in \gls{EU}.

		\begin{figure}[htbp!]
			\begin{center}
				\includegraphics[width=\columnwidth]{./images/eu_future/tailings.png}
			\end{center}
			\caption{Timeseries of Tailings Mass in the \gls{EU}.}
			\label{fig:eu_tail}
		\end{figure}

		\begin{figure}[htbp!]
			\begin{center}
				\includegraphics[width=\columnwidth]{./images/eu_future/total_fuel.png}
			\end{center}
			\caption{Timeseries of Total Fuel Usage in \gls{EU}.}
			\label{fig:eu_fuel}
		\end{figure}

		\begin{figure}[htbp!]
			\begin{center}
				\includegraphics[width=\columnwidth]{./images/eu_future/snf.png}
			\end{center}
			\caption{Timeseries of Used Nuclear Fuel in \gls{EU}.}
			\label{fig:eu_snf}
		\end{figure}
		\FloatBarrier

		\begin{table}[h]
			\centering
			\begin{tabular}{|c|c|c|}
				\hline
				Isotope & Mass Fraction in Used Fuel [\%] & Quantity [t] \\ \hline
				Total & .9358 & 1,473 \\ \hline
				Pu238 & .0111 & 17.47 \\ \hline
				Pu239 & .518 & 815.7 \\ \hline
				Pu240 & .232 & 365.33 \\ \hline
				Pu241 & .126 & 198.41 \\ \hline
				Pu242 & .0487 & 76.68 \\ \hline
			\end{tabular}
			\caption{Plutonium From Used Fuel}
			\label{tab:pu}
		\end{table}

		To create \gls{MOX} for an ASTRID, 11\% Pu and 89\% depleted uranium is used.
		Thus $1,473$ tons of plutonium yields $13,390$ tons of
		\gls{MOX}. \Cref{tab:pu} lists the isotope, mass fraction,
		and quantity of plutonium that can be obtained from the 2050 \gls{UNF} inventory.

@@

		From Varaine et al. \cite{marsaultmarie-sophie_pre-conceptual_2012}, a French
		ASTRID-type \gls{SFR} of capacity 600 MWe needs $1.225$ tons of
		plutonium a year, with an initial plutonium loading of $4.9$ tons. 
		Thus, the number of \glspl{SFR} that can be loaded with the reprocessed
		plutonium from \gls{UNF} can be estimated to $\frac{1,473}{4.9} \approx 300$ \glspl{SFR},
		assuming infinite reprocessing and fabrication capacity as well as
		abundant depleted uranium supply.

		Also, assuming that \gls{MOX} can be recycled indefinitely,
		used \gls{MOX} from an ASTRID reactor
		contains enough plutonium to produce a \gls{MOX} fuel with
		the same mass, if mixed with depleted uranium. For example,
		used \gls{MOX} from an ASTRID reactor is assumed to be 12.6\% plutonium
		in this simulation (see \cref{tab:comp}), whereas a fresh \gls{MOX} is 11\% plutonium.
		Separating plutonium from used \gls{MOX} from
		an ASTRID reactor can create \gls{MOX} of the mass of used \gls{MOX}.
		The plutonium breeding ratio in this simulation is thus assumed to be
		$\approx 1.145$.

		The second scenario, with the tailings and used \gls{UOX}
		inventory, evaluates if the French can transition into \gls{SFR}
		without constructing additional \gls{LWR}s. This simulation
		assumed infinite reprocessing and fabrication capacity.

		\Cref{fig:fuel} shows the timeseries mass of \gls{MOX} used in the 
		\gls{SFR}s separated by their origin.
		Note that the plot shows \gls{MOX}
		accumulation prior to \gls{SFR} deployment from 2020.

@@

		\Cref{fig:reprocess_waste} shows the amount of reprocessing waste
		(minor actinides, fission products) over time. Note that 
		reprocessing waste from \gls{UOX} reprocessing is substantially
		greater than waste from \gls{MOX} reprocessing due to its lower
		plutonium and uranium content.

		\Cref{fig:pu_isotopics} shows the isotopics of the plutonium that are
		reprocessed from the used fuel inventory.

		\begin{figure}[htbp!]
			\begin{center}
				\includegraphics[width=\columnwidth]{./images/french-transition/rep_pu.png}
			\end{center}
			\caption{Plutonium timeseries separated by isotope}
			\label{fig:pu_isotopics}
		\end{figure}

		\begin{figure}[htbp!]
			\begin{center}
				\includegraphics[width=\columnwidth]{./images/french-transition/reprocess_waste.png}
			\end{center}
			\caption{Reprocessing Waste for French Transition Scenario.}
			\label{fig:reprocess_waste}
		\end{figure}

		\begin{table}[h]
			\centering
			\scalebox{0.7}{
				\begin{tabular}{|c|c|c|}
					\hline
					Category & Unit & Value  \\ \hline
					Total MOX used & MTHM & 116,115  \\ \hline
					Total \glspl{SFR} Deployed & & 200 \\ \hline
					Total Plutonium Reprocessed & MTHM & 14,414 \\ \hline
					Total MOX from UOX Waste & MTHM & 9,729  \\ \hline
					Total MOX from MOX Waste & MTHM  & 150,426  \\ \hline
					Total Tailings used & MTHM & 105,664 \\ \hline
					Total legacy UNF reprocessed & MTHM & 97,298 \\ \hline
					Total Reprocessed Uranium Stockpile & MTHM & 251,100 \\ \hline
					Total Reprocess Waste & MTHM & 14,414 \\ \hline
				\end{tabular}}
				\caption {\gls{SFR} Simulation Results}
				\label{tab:sfr_sim_result}
				\end {table}
